### 2020-01-31 ncov.tex
minor tweaks

For each study, we construct a family of parameter sets by drawing 100,000 random samples from the probability distributions (Table 2) that represent the estimates of \Ro and the assumed values of $\bar G$ and $\kappa$ and calculating the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_i = \frac{{\mathcal R_{0i}}^{\kappa_i} - 1}{\kappa_i \bar{G}_i}.
\end{equation}
\end{linenomath*}
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study;
uncertainties in the probability distributions that we calculate for the estimated exponential growth rates will reflect the methods and assumptions that the studies rely on.

>>>>

For each study $i$, we construct a family of parameter sets by drawing 100,000 random samples from the probability distributions (Table 2) that represent the estimates of $\mathcal R_{0i}$ and the assumed values of $\bar G_i$ and $\kappa_i$ and calculating the exponential growth rate $r_i$ via the inverse of \eref{gamma}:
\begin{linenomath*}
\begin{equation}
r_i = \frac{{\mathcal R_{0i}}^{\kappa_i} - 1}{\kappa_i \bar{G}_i}.
\end{equation}
\end{linenomath*}
This allows us to approximate the probability distributions of the estimated exponential growth rates by each study;
uncertainties in the probability distributions that we calculate for the estimated exponential growth rates will reflect the methods and assumptions that the studies rely on.
